%\newpage

\cvsection{Poster Presentations}

%-------------------------------------------------------------------------------

\begin{cvpubs}
    \cvpub
        {\textbf{McDaniel, E.A.}, Moya, F., Camejo, P., He, S., McMahon, K.D. Long-Term Population Dynamics of 'Candidatus Accumulibacter phosphatis' in Enhanced Biological Phosphorus Removal Sequencing-Batch Reactors. Population, Evolutionary, Quantitative Genetics Conference. Madison, WI. May 2018.} % Ref
        {7.} % Number
    \cvpub
        {\textbf{McDaniel, E.A.}, Peterson, B., Stevens, S.L.R., Krabbenhoft, D., McMahon, K.D. Comparative Genomics of Microbial Methylmercury Production. Madison Microbiome Meeting. Madison, WI. Apr. 2018.} % Ref
        {6.} % Number
    \cvpub
        {\textbf{McDaniel, E.A.}, Peterson, B., Stevens, S.L.R., Krabbenhoft, D., McMahon, K.D. Comparative Genomics of Microbial Methylmercury Production. Joint Genome Institute User Meeting: Genomics of Energy and Environment. San Francisco, CA. Mar. 2018.} % Ref
        {5.} % Number
    \cvpub
        {\textbf{McDaniel, E.A.}, Stuecker, T.N., Elkon, I.M., Gasch, A.P., Lewis, J.A. Natural Variation in Yeast Uncovers Novel Regulation of the Ena1p Sodium Pump. Arkansas IDeA Network of Biomedical Research Excellence Meeting. Fayetteville, AR. Nov. 2015.}       
        {4.}
    \cvpub
        {\textbf{McDaniel, E.A.}, Stuecker, T.N., Elkon, I.M., Gasch, A.P., Lewis, J.A. Natural Variation in Yeast Uncovers Novel Regulation of the Ena1p Sodium Pump. 27th International Conference on Yeast Genetics and Molecular Biology. Levico Terme, Trentinto, Italy. Sept. 2015.}
        {3.}
\end{cvpubs}
\newpage
%-------------------------------------------------------------------------------
% To force the pagebreak
%-------------------------------------------------------------------------------
\begin{cvpubs}
    \cvpub
        {\textbf{McDaniel, E.A.}, Stuecker, T.N., Elkon, I.M., Gasch, A.P., Lewis, J.A. Natural Variation in Yeast Uncovers Novel Regulation of the Ena1p Sodium Pump.South Central Branch of the American Society for Microbiology Joint Meeting. Fayetteville, AR. Sept. 2014.}
        {2.}
    \cvpub
        {\textbf{McDaniel, E.A.}, Rutledge, M.T., Broach, J.R. Chromosome Interactions in Quiescent Yeast. Penn State Hershey Summer Undergraduate Research Internship Programs Symposium. Hershey, PA. Aug. 2014.}
        {1.}
\end{cvpubs}
