%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant} % Job title
    {McMahon Lab, University of Wisconsin-Madison} % Organization
    {Madison, WI} % Location
    {Jan. 2017 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Graduate research assistant in the laboratory of Dr. Katherine McMahon investigating bacterial communities in freshwater ecosystems and engineered wastewater systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Research Assistnat} % Job title
    {Lewis Lab, University of Arkansas} % Organization
    {Fayetteville, AR} % Location
    {Aug.2013-Aug.2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Undergraduate research assistant in the laboratory of Dr. Jeffrey Lewis studying the natural variation of stress defense mechanisms in the budding yeast Saccharomyces cerevisiae.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Research Intern} % Job title
    {Broach Lab, Penn State Hershey College of Medicine} % Organization
    {Hershey, PA} % Location
    {May-Aug. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Intern in the Summer Undergraduate Research Internship Program in the laboratory of Dr. James Broach studying the interactions and movements of chromosomes during quiescence in the budding yeast Saccharomyces cerevisiae.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
