%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Teaching, Mentoring, \& Service}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Teaching Assistant} % Affiliation/role
    {Microbiology 304: Biology of Microorganisms Laboratory} % Organization/group
    {Madison, WI} % Location
    {Spring 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Prepared lecture materials on the background, significance, and execution of experiments twice a week.}
        \item {Assisted students with experiments and provided feedback on techniques and scientific analyses.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Student Mentor for REUs and Undergraduate Interns} % Affiliation/role
    {McMahon Lab Mentoring} % Organization/group
    {Madison, WI} % Location
    {2017-present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Graduate Student mentor for summer REU and Undergraduate Interns performing routine fieldwork and independent research projects in the McMahon lab.}
        \item {\textbf{Kaela Amundson:} Characterization and Enrichment of External Electron Transfer Capable Microorganisms. Fall 2017-Spring 2018. Mentored Kaela through laboratory protocols, bioinformatic pipelines, graduate school applications, and a National Science Foundation Graduate Research Fellowship application.}
        \item {\textbf{Matthew Wolff:} Investigation of Zebra Mussel eDNA in Lake Mendota Metagenomic Time-series Datasets. Spring 2018-current. Mentored Matthew through laboratory techniques and bioinformatic pipelines.}
        \item {\textbf{Kali Denis:} Time-Series Analysis of Under-Ice Freshwater Bacterial Communities. Spring 2018-current. Mentored Kali through laboratory protocols, design and execution of an independent project, and preparation of a UW-Madison Sophomore Research Fellowship.}
      \end{cvitems}
    }

  %---------------------------------------------------------
    \cventry
    {Co-Chair} % Affiliation/role
    {Computational Biology, Ecology, \& Evolution (ComBEE) Study Group} % Organization/group
    {Madison, WI} % Location
    {Jan. 2017-present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Organized peer-led discussions on the R and Python languages.}
        \item {Facilitated monthly meetings in which a postdoc/faculty member gives a talk on their research.}
        \item {Lead ComBEE hosted workshops on computational tools (Git/Anvi'o)}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Workshop Leader} % Affiliation/role
    {ComBEE Git/Github Pages Workshop} % Organization/group
    {Madison, WI} % Location
    {Sept. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Prepared novel materials and taught version control with Git and making a personal website using Github Pages/Jekyll.}
        \item {Led a walkthrough tutorial to a group of 10 scientists on making a personal website with Github Pages.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Workshop Assistant} % Affiliation/role
    {ComBEE Anvi'o Workshop} % Organization/group
    {Madison, WI} % Location
    {May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Assisted during a ComBEE hosted workshop on the Anvi'o software.}
        \item {Guided participants through the interactive interface and metagenomic binning tutorials.}
        \item {Led an informal presentation and discussion on the theory of metagenomic binning.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Drill instructor} % Affiliation/role
    {BIOL 2323: General Genetics} % Organization/group
    {Fayetteville, AR} % Location
    {Sp. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Instructor and leader of biweekly review sessions for an undergraduate General Genetics course.}
        \item {Prepared biweekly overviews of lecture materials and exam study guides.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student Ambassador} % Affiliation/role
    {University of Arkansas Office of Admissions} % Organization/group
    {Fayetteville, AR} % Location
    {Fa. 2013-2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Volunteered 2 hours a week guiding tours of the University of Arkansas campus and housing options to prospective students.}
        \item {Wrote thank-you notest to the students and families that visited campus.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
