%\newpage

\cvsection{Presentations}

%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------

\begin{cvpubs}
    \cvpub
        {\textbf{McDaniel, E.A.}, Stuecker, T.N., Elkon, I.M., Gasch, A.P., Lewis, J.A. Natural Variation in Yeast Uncovers Novel Regulation of the Ena1p Sodium Pump. Southeastern Regional Yeast Meeting. Tuscaloosa, AL. Mar. 2016. \textbf{Platform Talk.}} % Ref
        {6.} % Number
        \cvpub
        {\textbf{McDaniel, E.A.}, Stuecker, T.N., Elkon, I.M., Gasch, A.P., Lewis, J.A. Natural Variation in Yeast Uncovers Novel Regulation of the Ena1p Sodium Pump. Arkansas IDeA Network of Biomedical Research Excellence Meeting. Fayetteville, AR. Nov. 2015. \textbf{Poster Presentation.}}       
        {5.}
    \cvpub
        {\textbf{McDaniel, E.A.}, Stuecker, T.N., Elkon, I.M., Gasch, A.P., Lewis, J.A. Natural Variation in Yeast Uncovers Novel Regulation of the Ena1p Sodium Pump. 27th International Conference on Yeast Genetics and Molecular Biology. Levico Terme, Trentinto, Italy. Sept. 2015. \textbf{Poster Presentation.}}
        {4.}
        \cvpub
        {\textbf{McDaniel, E.A.}, Stuecker, T.N., Elkon, I.M., Gasch, A.P., Lewis, J.A. Natural Variation in Yeast Uncovers Novel Regulation of the Ena1p Sodium Pump. Southeastern Regional Yeast Meeting. Little Rock, AR. Mar. 2015. \textbf{Platform Talk.}}
        {3.}
    \cvpub
        {\textbf{McDaniel, E.A.}, Stuecker, T.N., Elkon, I.M., Gasch, A.P., Lewis, J.A. Natural Variation in Yeast Uncovers Novel Regulation of the Ena1p Sodium Pump.South Central Branch of the American Society for Microbiology Joint Meeting. Fayetteville, AR. Sept. 2014. \textbf{Poster Presentation.}}
        {2.}
    \cvpub
        {\textbf{McDaniel, E.A.}, Rutledge, M.T., Broach, J.R. Chromosome Interactions in Quiescent Yeast. Penn State Hershey Summer Undergraduate Research Internship Programs Symposium. Hershey, PA. Aug. 2014. \textbf{Poster Presentation.}}
        {1.}
\end{cvpubs}
